---
title: "isogut_fin"
output: html_document
date: "2026-04-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(vegan)
library(lme4)
library(ggrepel)
library(readxl)
library(lubridate)
library(patchwork)
```

# data load 

```{r, data cleanin}
# ============================================================
# SET FILE PATHS HERE
# ============================================================
path_gut_content <- "BOEM_GC_Analysis(Sheet1).csv"
path_tissue_log  <- "/Users/graciesemmens/Downloads/Ramirez_FishTissue_Master_File(Tissue_Log).csv"
path_isotope     <- "/Users/graciesemmens/Downloads/_metadata(bulk_CN_data).csv"
path_nicerover   <- "/Users/graciesemmens/Downloads/NicheROVER_overlap.xlsx"

# load raw data
df_raw <- read.csv(path_gut_content)

# fix known species ID errors
df_raw$Fish.Species[df_raw$Fish.ID == "LIZ020"]   <- "Lizardfish"
df_raw$Fish.Species[df_raw$Fish.ID == "ATB046gc"]  <- "Atlantic Bumper"
df_raw$Fish.Species[df_raw$Fish.ID == "PIN 173"]   <- "Pinfish"

# rename columns
df <- df_raw %>%
  rename(
    fish_species     = Fish.Species,
    fish_id          = Fish.ID,
    stomach_id       = Stomach.ID,
    site             = Site,
    collection_date  = Collection.Date,
    prey_wet_weight  = Prey.Wet.Weight..g.,
    prey_category    = Prey,
    n_prey           = X..Prey,
    prey_condition   = Prey.Conditions..1.5.,
    notes            = Notes
  )

# remove blank prey rows
df <- df %>%
  mutate(
    prey_category = str_trim(prey_category),
    prey_category = na_if(prey_category, "")
  ) %>%
  filter(!is.na(prey_category))

# standardize prey names
df <- df %>%
  mutate(
    fish_id = str_trim(fish_id),
    prey_category_clean = str_trim(tolower(prey_category)),
    prey_category_clean = case_when(
      prey_category_clean %in% c("crustcacean", "crustcean", 
                                  "crustacean based biomatter")       ~ "crustacean",
      prey_category_clean %in% c("mollusc", "molusca", 
                                  "squid (mollusca)", "squid")        ~ "mollusca",
      prey_category_clean %in% c("biomattter", 
                                  "biomatter, very weird bone thing",
                                  "unidentifiable fish?",
                                  "unidentifiable fish")              ~ "biomatter",
      prey_category_clean == "polycheate"                             ~ "polychaete",
      prey_category_clean == "detritus + maybe a shell"               ~ "detritus",
      prey_category_clean == "striped anchovy"                        ~ "anchovy",
      TRUE ~ prey_category_clean
    )
  )

# remove unknown species
df_clean <- df %>%
  mutate(
    fish_species = str_trim(fish_species),
    fish_species = na_if(fish_species, "Not found")
  ) %>%
  filter(!is.na(fish_species))

# parse site codes
df_clean <- df_clean %>%
  mutate(
    site     = str_trim(toupper(site)),
    region   = case_when(
      str_starts(site, "E") ~ "East",
      str_starts(site, "W") ~ "West",
      TRUE ~ NA_character_
    ),
    position = case_when(
      str_detect(site, "I") ~ "Inner",
      str_detect(site, "O") ~ "Outer",
      TRUE ~ NA_character_
    )
  )

# fix collection dates (Excel serial numbers)
df_raw <- df_raw %>%
  mutate(
    collection_date_clean = case_when(
      str_detect(as.character(Collection.Date), "/") ~
        as.Date(as.character(Collection.Date), format = "%m/%d/%Y"),
      str_detect(as.character(Collection.Date), "^11082024$") ~
        as.Date("2024-11-08"),
      TRUE ~ as.Date(as.numeric(as.character(Collection.Date)),
                     origin = "1899-12-30")
    )
  )

df_clean <- df_clean %>%
  left_join(
    df_raw %>%
      mutate(fish_id = str_trim(Fish.ID)) %>%
      select(fish_id, collection_date_clean) %>%
      distinct(),
    by = "fish_id"
  ) %>%
  mutate(collection_date = collection_date_clean) %>%
  select(-collection_date_clean)

cat("Total fish:", n_distinct(df_clean$fish_id), "\n")
cat("Total species:", n_distinct(df_clean$fish_species), "\n")
```

# FOO 

```{r FOO}
# load tissue log for true denominators
tissue_log  <- read.csv(path_tissue_log)
tissue_boem <- tissue_log %>%
  filter(Project == "BOEM") %>%
  mutate(sample_id = str_trim(sample.id))

# true denominator per species
n_stomachs_true <- tissue_boem %>%
  filter(!str_detect(species, "Unknown")) %>%
  group_by(species) %>%
  summarise(n_stomachs_total = n_distinct(sample_id), .groups = "drop") %>%
  rename(fish_species = species) %>%
  mutate(n_stomachs_total = case_when(
    fish_species == "Pigfish" ~ 35L,
    TRUE ~ n_stomachs_total
  ))

# FOO - all prey
unidentifiable <- c("unidentifiable mush", "biomatter")

foo <- df_clean %>%
  filter(!is.na(prey_category_clean)) %>%
  group_by(fish_species, fish_id) %>%
  summarise(prey_cats = list(unique(prey_category_clean)), .groups = "drop") %>%
  unnest(prey_cats) %>%
  group_by(fish_species, prey_cats) %>%
  summarise(n_stomachs_with_prey = n(), .groups = "drop") %>%
  left_join(n_stomachs_true, by = "fish_species") %>%
  mutate(FOO_percent = (n_stomachs_with_prey / n_stomachs_total) * 100) %>%
  arrange(fish_species, desc(FOO_percent))

# FOO - identifiable prey only
foo_id <- df_clean %>%
  filter(!is.na(prey_category_clean),
         !prey_category_clean %in% unidentifiable) %>%
  group_by(fish_species, fish_id) %>%
  summarise(prey_cats = list(unique(prey_category_clean)), .groups = "drop") %>%
  unnest(prey_cats) %>%
  group_by(fish_species, prey_cats) %>%
  summarise(n_stomachs_with_prey = n(), .groups = "drop") %>%
  left_join(n_stomachs_true, by = "fish_species") %>%
  mutate(FOO_percent = (n_stomachs_with_prey / n_stomachs_total) * 100) %>%
  arrange(fish_species, desc(FOO_percent))
```

# Dietary Diversity Metrics

```{r diversity}
foo_diversity <- foo_id %>%
  group_by(fish_species) %>%
  summarise(
    prey_richness = n(),
    shannon  = -sum((FOO_percent/100) * log(FOO_percent/100)),
    simpson  = 1 - sum((FOO_percent/100)^2),
    evenness = shannon / log(prey_richness),
    .groups  = "drop"
  ) %>%
  arrange(desc(shannon))

print(foo_diversity)
```

# Prey Matrix and PERMANOVA

```{r prey_matrix}
# build presence-absence prey matrix
prey_matrix <- df_clean %>%
  filter(!is.na(prey_category_clean)) %>%
  distinct(fish_id, fish_species, region, collection_date,
           position, prey_category_clean) %>%
  mutate(present = 1) %>%
  pivot_wider(
    id_cols     = c(fish_id, fish_species, region,
                    collection_date, position),
    names_from  = prey_category_clean,
    values_from = present,
    values_fill = 0
  )

# add corrected dates
fish_dates <- df_clean %>%
  group_by(fish_id) %>%
  summarise(collection_date = first(na.omit(collection_date)),
            .groups = "drop")

prey_matrix <- prey_matrix %>%
  select(-collection_date) %>%
  left_join(fish_dates, by = "fish_id")

prey_cols <- prey_matrix %>%
  select(-fish_id, -fish_species, -region, -collection_date, -position)
```

```{r permanova_main}
# species
adonis2(prey_cols ~ fish_species, data = prey_matrix, permutations = 999)

# collection date
prey_matrix_date <- prey_matrix %>% filter(!is.na(collection_date))
prey_cols_date   <- prey_matrix_date %>%
  select(-fish_id, -fish_species, -region, -collection_date, -position)
adonis2(prey_cols_date ~ collection_date, 
        data = prey_matrix_date, permutations = 999)

# full model
prey_matrix_full <- prey_matrix %>%
  filter(!is.na(position) & !is.na(region) & !is.na(collection_date))
prey_cols_full <- prey_matrix_full %>%
  select(-fish_id, -fish_species, -region, -collection_date, -position)
adonis2(prey_cols_full ~ fish_species + region + position + collection_date,
        data = prey_matrix_full, permutations = 999)
```

```{r permanova_regional}
# pairwise regional PERMANOVA per species
results_regional <- prey_matrix %>%
  filter(!is.na(region)) %>%
  group_by(fish_species) %>%
  group_map(~ {
    cols <- .x %>% select(-fish_id, -fish_species, -region, 
                          -collection_date, -position)
    if (n_distinct(.x$region) < 2 || nrow(.x) < 5) return(NULL)
    result <- adonis2(cols ~ region, data = .x, permutations = 999)
    tibble(fish_species = unique(.x$fish_species),
           F_stat = result$F[1], R2 = result$R2[1],
           p_value = result$`Pr(>F)`[1], n = nrow(.x))
  }, .keep = TRUE) %>%
  bind_rows() %>%
  arrange(p_value)

print(results_regional)
```

```{r permanova_ontogenetic}
# ontogenetic PERMANOVA per species
individual_size <- tissue_boem %>%
  mutate(fish_id  = str_trim(sample_id),
         TL_mm    = suppressWarnings(as.numeric(TL.mm))) %>%
  select(fish_id, TL_mm)

prey_matrix_size <- prey_matrix %>%
  left_join(individual_size, by = "fish_id")

results_ontogenetic <- prey_matrix_size %>%
  filter(!is.na(TL_mm)) %>%
  group_by(fish_species) %>%
  group_map(~ {
    cols <- .x %>%
      select(-fish_id, -fish_species, -TL_mm,
             -region, -collection_date, -position) %>%
      mutate(across(everything(), ~replace_na(., 0)))
    if (nrow(.x) < 10) return(NULL)
    result <- adonis2(cols ~ TL_mm, data = .x, permutations = 999)
    tibble(fish_species = unique(.x$fish_species),
           F_stat = result$F[1], R2 = result$R2[1],
           p_value = result$`Pr(>F)`[1], n = nrow(.x))
  }, .keep = TRUE) %>%
  bind_rows() %>%
  arrange(p_value)

print(results_ontogenetic)
```

```{r permanova_seasonal}
# seasonal PERMANOVA per species
prey_matrix_season <- prey_matrix %>%
  left_join(
    df_clean %>%
      mutate(season = case_when(
        month(collection_date) %in% c(12,1,2,3) ~ "Winter",
        month(collection_date) %in% c(4,5)      ~ "Spring",
        month(collection_date) %in% c(6,7,8)    ~ "Summer",
        month(collection_date) %in% c(9,10,11)  ~ "Fall"
      )) %>%
      group_by(fish_id) %>%
      summarise(season = first(season), .groups = "drop"),
    by = "fish_id"
  )

results_seasonal <- prey_matrix_season %>%
  filter(!is.na(season)) %>%
  group_by(fish_species) %>%
  group_map(~ {
    cols <- .x %>%
      select(-fish_id, -fish_species, -region,
             -collection_date, -position, -season) %>%
      mutate(across(everything(), ~replace_na(., 0)))
    if (nrow(.x) < 10 || n_distinct(.x$season) < 2) return(NULL)
    result <- adonis2(cols ~ season, data = .x, permutations = 999)
    tibble(fish_species = unique(.x$fish_species),
           F_stat = result$F[1], R2 = result$R2[1],
           p_value = result$`Pr(>F)`[1], n = nrow(.x))
  }, .keep = TRUE) %>%
  bind_rows() %>%
  arrange(p_value)

print(results_seasonal)
```

# NMDS Dietary Niche Space

```{r nmds}
species_matrix <- foo_id %>%
  select(fish_species, prey_cats, FOO_percent) %>%
  pivot_wider(names_from = prey_cats, values_from = FOO_percent,
              values_fill = 0) %>%
  column_to_rownames("fish_species")

set.seed(123)
nmds <- metaMDS(species_matrix, distance = "bray", k = 2)
cat("NMDS stress:", round(nmds$stress, 3), "\n")

nmds_scores <- as.data.frame(scores(nmds)) %>%
  rownames_to_column("fish_species") %>%
  left_join(foo_diversity, by = "fish_species")

ggplot(nmds_scores, aes(x = sites.NMDS1, y = sites.NMDS2)) +
  geom_point(aes(size = shannon, color = fish_species), alpha = 0.7) +
  geom_text_repel(aes(label = fish_species), size = 3.5,
                  box.padding = 0.5, point.padding = 0.3) +
  scale_size_continuous(name = "Shannon\nDiversity", range = c(3, 12)) +
  guides(color = "none") +
  labs(title    = "Dietary Niche Space by Species",
       subtitle = paste0("NMDS stress = ", round(nmds$stress, 3)),
       x = "NMDS1", y = "NMDS2") +
  theme_minimal(base_size = 12) +
  coord_cartesian(ylim = c(-0.5, 0.65))

ggsave("dietary_niche_nmds.png", width = 10, height = 7, dpi = 300)
```

# Iso Data Prep

```{r isotopes}
isotope_raw <- read.csv(path_isotope)

isotope_clean <- isotope_raw %>%
  filter(!str_detect(fish.id, "LIZ")) %>%
  mutate(tray_date = as.numeric(str_extract(tray, "^[0-9]+"))) %>%
  arrange(fish.id, desc(tray_date)) %>%
  distinct(fish.id, .keep_all = TRUE) %>%
  select(fish_id = fish.id, d13C, d15N) %>%
  mutate(fish_species = case_when(
    str_starts(fish_id, "ATB") ~ "Atlantic Bumper",
    str_starts(fish_id, "CRO") ~ "Atlantic Croaker",
    str_starts(fish_id, "MOF") ~ "Moonfish",
    str_starts(fish_id, "PIG") ~ "Pigfish",
    str_starts(fish_id, "PIN") ~ "Pinfish",
    str_starts(fish_id, "SPO") ~ "Spot",
    str_starts(fish_id, "STA") ~ "Striped Anchovy",
    str_starts(fish_id, "THH") ~ "Thread Herring",
    str_starts(fish_id, "WEF") ~ "Weakfish"
  ))

# center within species
isotope_centered <- isotope_clean %>%
  group_by(fish_species) %>%
  mutate(
    d15N_centered = d15N - mean(d15N, na.rm = TRUE),
    d13C_centered = d13C - mean(d13C, na.rm = TRUE)
  ) %>%
  ungroup()

cat("Isotope samples per species:\n")
print(isotope_clean %>% count(fish_species))
```

# SQ1 — Do Dietary Outliers Correspond to Isotopic Outliers?

```{r sq1}
# individual NMDS
set.seed(123)
nmds_ind <- metaMDS(prey_cols, distance = "bray", k = 2, trymax = 100)

# dietary distance from species centroid
ind_nmds <- as.data.frame(scores(nmds_ind, display = "sites")) %>%
  bind_cols(prey_matrix %>% select(fish_id, fish_species)) %>%
  group_by(fish_species) %>%
  mutate(
    centroid_NMDS1 = mean(NMDS1),
    centroid_NMDS2 = mean(NMDS2),
    gut_dist = sqrt((NMDS1 - centroid_NMDS1)^2 +
                    (NMDS2 - centroid_NMDS2)^2)
  ) %>%
  ungroup()

# isotopic distance from species centroid
iso_dist_df <- isotope_clean %>%
  filter(fish_species != "Pigfish") %>%
  group_by(fish_species) %>%
  mutate(
    centroid_d13C = mean(d13C, na.rm = TRUE),
    centroid_d15N = mean(d15N, na.rm = TRUE),
    iso_dist = sqrt((d13C - centroid_d13C)^2 +
                    (d15N - centroid_d15N)^2)
  ) %>%
  ungroup()

# join
ind_combined <- ind_nmds %>%
  inner_join(iso_dist_df %>% select(fish_id, fish_species, iso_dist),
             by = c("fish_id", "fish_species")) %>%
  filter(fish_species != "Pigfish")

cat("SQ1 n =", nrow(ind_combined), "\n")

# random intercept model
model_q1 <- lmer(iso_dist ~ gut_dist + (1 | fish_species),
                 data = ind_combined)
summary(model_q1)

# within-species spearman as confirmatory check
ind_combined %>%
  group_by(fish_species) %>%
  summarise(rho = cor(gut_dist, iso_dist, method = "spearman"), n = n())
```

# SQ2 — Does δ¹⁵N Reflect Trophic Level of Diet?

```{r sq2}
prey_traits <- data.frame(
  prey_category_clean = c("veg_biomatter", "detritus", "mollusca",
                          "echinoderm", "polychaete", "crustacean",
                          "anchovy", "thread herring", "cnidarian",
                          "synthetic material", "biomatter",
                          "unidentifiable mush"),
  trophic_level = c(1.0, 1.0, 2.1, 2.1, 2.2, 2.6, 3.1, 3.1,
                    2.6, NA, NA, NA),
  energy_source = c("benthic", "benthic", "benthic", "benthic",
                    "benthic", "mixed", "pelagic", "pelagic",
                    "pelagic", NA, NA, NA)
)

ind_trophic <- df_clean %>%
  left_join(prey_traits, by = "prey_category_clean") %>%
  filter(!is.na(trophic_level)) %>%
  group_by(fish_id, fish_species) %>%
  summarise(
    mean_TL      = mean(trophic_level, na.rm = TRUE),
    prop_benthic = mean(energy_source == "benthic", na.rm = TRUE),
    .groups = "drop"
  )

ind_trophic_iso_centered <- ind_trophic %>%
  filter(fish_species != "Pigfish") %>%
  inner_join(isotope_centered %>%
               select(fish_id, fish_species,
                      d15N_centered, d13C_centered),
             by = c("fish_id", "fish_species"))

cat("SQ2/SQ3 n =", nrow(ind_trophic_iso_centered), "\n")

# spearman
cor.test(ind_trophic_iso_centered$mean_TL,
         ind_trophic_iso_centered$d15N_centered,
         method = "spearman")

# linear regression
model_TL <- lm(d15N_centered ~ mean_TL, data = ind_trophic_iso_centered)
summary(model_TL)
```

# SQ3 — Does δ¹³C Reflect Benthic vs Pelagic Diet?

```{r sq3}
# spearman
cor.test(ind_trophic_iso_centered$prop_benthic,
         ind_trophic_iso_centered$d13C_centered,
         method = "spearman")

# linear regression
model_C <- lm(d13C_centered ~ prop_benthic, data = ind_trophic_iso_centered)
summary(model_C)
```

# Combined Assumption Test Figure

```{r combined_figure}
p_divergence <- ggplot(ind_combined,
                       aes(x = gut_dist, y = iso_dist,
                           color = fish_species)) +
  geom_point(alpha = 0.3, size = 1) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
  facet_wrap(~fish_species, scales = "free", nrow = 1) +
  labs(x = "Distance from gut content centroid (NMDS)",
       y = "Distance from\nisotopic centroid (‰)", tag = "A") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none",
        strip.text = element_text(size = 8, face = "bold"),
        plot.tag = element_text(face = "bold"))

p_TL <- ggplot(ind_trophic_iso_centered,
               aes(x = mean_TL, y = d15N_centered,
                   color = fish_species)) +
  geom_point(alpha = 0.3, size = 1) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
  facet_wrap(~fish_species, scales = "free", nrow = 1) +
  labs(x = "Mean trophic level of gut contents",
       y = "δ¹⁵N centered (‰)", tag = "B") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none",
        strip.text = element_text(size = 8, face = "bold"),
        plot.tag = element_text(face = "bold"))

p_C <- ggplot(ind_trophic_iso_centered,
              aes(x = prop_benthic, y = d13C_centered,
                  color = fish_species)) +
  geom_point(alpha = 0.3, size = 1) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
  facet_wrap(~fish_species, scales = "free", nrow = 1) +
  labs(x = "Proportion benthic prey in gut contents",
       y = "δ¹³C centered (‰)", tag = "C") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none",
        strip.text = element_text(size = 8, face = "bold"),
        plot.tag = element_text(face = "bold"))

combined_figure <- p_divergence / p_TL / p_C +
  plot_annotation(
    title   = "Testing core assumptions of stable isotope trophic ecology",
    caption = "A: SQ1 individual dietary vs isotopic divergence (n = 1001)\nB: SQ2 δ¹⁵N vs mean trophic level (n = 470)\nC: SQ3 δ¹³C vs proportion benthic prey (n = 470)",
    theme = theme(plot.title   = element_text(size = 13, face = "bold"),
                  plot.caption = element_text(size = 8, hjust = 0))
  )

ggsave("isotope_assumptions_combined.png", combined_figure,
       width = 16, height = 14, dpi = 300)
```

# Species-level Niche Comparison (Shannon vs SEA.c)

```{r niche_comparison}
sea_c <- data.frame(
  fish_species = c("Atlantic Bumper", "Atlantic Croaker", "Moonfish",
                   "Pinfish", "Spot", "Striped Anchovy",
                   "Thread Herring", "Weakfish"),
  SEA_c = c(0.868, 5.490, 2.029, 6.270, 11.151, 3.352, 5.144, 12.404)
)

niche_comparison <- foo_diversity %>%
  filter(fish_species %in% sea_c$fish_species) %>%
  left_join(sea_c, by = "fish_species")

cor.test(niche_comparison$shannon, niche_comparison$SEA_c,
         method = "spearman")

ggplot(niche_comparison, aes(x = shannon, y = SEA_c)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_text_repel(aes(label = fish_species), size = 3.5) +
  labs(x = "Dietary Shannon Diversity (FOO-based)",
       y = "Isotopic Niche Size (SEA.c, ‰²)",
       title    = "Dietary breadth vs isotopic niche space",
       subtitle = "Spearman rho = 0.60, p = 0.13, n = 8") +
  theme_minimal(base_size = 12)

ggsave("dietary_vs_isotopic_niche.png", width = 8, height = 6, dpi = 300)
```

# Dietary vs Isotopic Overlap (NicheROVER)

```{r nicerover}
nicerover_raw <- read_excel(path_nicerover, sheet = "Mean 0.95")

nicerover_long <- nicerover_raw %>%
  rename(species1 = Species) %>%
  pivot_longer(-species1, names_to = "species2",
               values_to = "overlap_raw") %>%
  filter(overlap_raw != "NA ") %>%
  mutate(isotopic_overlap_AB = as.numeric(str_extract(overlap_raw, "^[0-9.]+"))) %>%
  select(species1, species2, isotopic_overlap_AB)

nicerover_sym <- nicerover_long %>%
  left_join(nicerover_long %>%
              rename(species2 = species1, species1 = species2,
                     isotopic_overlap_BA = isotopic_overlap_AB),
            by = c("species1", "species2")) %>%
  mutate(isotopic_overlap = (isotopic_overlap_AB + isotopic_overlap_BA) / 2) %>%
  filter(species1 < species2) %>%
  select(species1, species2, isotopic_overlap)

dietary_overlap <- vegdist(species_matrix, method = "bray") %>%
  as.matrix() %>% as.data.frame() %>%
  rownames_to_column("species1") %>%
  pivot_longer(-species1, names_to = "species2",
               values_to = "dietary_dissimilarity") %>%
  mutate(dietary_similarity = 1 - dietary_dissimilarity) %>%
  filter(species1 < species2)

overlap_comparison <- dietary_overlap %>%
  inner_join(nicerover_sym, by = c("species1", "species2"))

cor.test(overlap_comparison$dietary_similarity,
         overlap_comparison$isotopic_overlap,
         method = "spearman")

ggplot(overlap_comparison, aes(x = dietary_similarity,
                                y = isotopic_overlap)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_text_repel(aes(label = paste(species1, "vs", species2)),
                  size = 2.5, max.overlaps = 20) +
  labs(x = "Dietary similarity (1 - Bray-Curtis)",
       y = "Isotopic niche overlap (NicheROVER, %)",
       title    = "Dietary vs isotopic niche overlap",
       subtitle = "Spearman rho = -0.10, p = 0.61, n = 28") +
  theme_minimal(base_size = 11)

ggsave("dietary_vs_isotopic_overlap.png", width = 10, height = 7, dpi = 300)
```

# Output Tables

```{r tables}
write_csv(foo_diversity,      "table_dietary_diversity.csv")
write_csv(results_regional,   "table_regional_permanova.csv")
write_csv(results_ontogenetic,"table_ontogenetic_permanova.csv")
write_csv(results_seasonal,   "table_seasonal_permanova.csv")
write_csv(niche_comparison,   "table_niche_comparison.csv")
write_csv(overlap_comparison, "table_dietary_isotopic_overlap.csv")

cat("All tables saved.\n")
```